---
title: "GIPCR"
author: "MayarAl Mohajer"
date: "3/2/2022"
output:
  pdf_document: default
  word_document: default
  html_document: default
---


Read Data 



```{r }
library("readxl")
GIPCR <- read_excel("GIPCR.xlsx",skip=1)
```

Describe data 

```{r}
library(psych)
describe(GIPCR)

table(GIPCR$`Study Period`)
table(GIPCR$`Stool Culture Ordered`)
table(GIPCR$`Stool Culture Results`)
table(GIPCR$`GI Panel Ordered`)
table(GIPCR$`GI Panel Results`)
table(GIPCR$`Abx of interest Ordered?`)
table(GIPCR$`Patient Days Present`)
table(GIPCR$`GI Panel Results`,GIPCR$`Study Period`)
table(GIPCR$`Abx of interest Ordered?`,GIPCR$`Study Period`)


```

Changing Negative to No for stool culture ordered 
Remove duplicate from Stool culture result 
Changing NO GI Perfomred to No in GI Panel performed 
Replace outpatient collect  in Patient Days Present with NA. Chanding it to numeric and obtaining summary

```{r}

GIPCR$`Stool Culture Ordered` <- gsub("Negative", "NO", GIPCR$`Stool Culture Ordered`)
table(GIPCR$`Stool Culture Ordered`)
GIPCR$`Stool Culture Results` <- gsub("No organism detected;  No organism detected", "No organism detected", GIPCR$`Stool Culture Results`)
table(GIPCR$`Stool Culture Results`)
GIPCR$`GI Panel Ordered` <- gsub("No GI Panel Performed", "NO", GIPCR$`GI Panel Ordered`)
table(GIPCR$`GI Panel Ordered`)
GIPCR$`Patient Days Present` <- gsub("outpatient collect", "NA", GIPCR$`Patient Days Present`)
GIPCR$`Patient Days Present` <- as.numeric(GIPCR$`Patient Days Present`)
summary(GIPCR$`Patient Days Present`)


```


Antibiotic use description 

```{r}

summary(GIPCR$DOT)
summary(GIPCR$LOT)
hist(GIPCR$DOT)
hist(GIPCR$DOT,main ="Days of therapy",xlab="Days of therapy",breaks =30)
hist(GIPCR$LOT,main ="Length of therapy",xlab="Length of therapy",breaks =30)

```

Data not normally distrbuted (mean different from median, right tail). 


Create new varibales for DOT per Patient Days Present and DOT per Patient Days Present

```{r}
GIPCR$DOTperPDP <- round(GIPCR$DOT/GIPCR$`Patient Days Present`,2)
GIPCR$LOTperPDP <- round(GIPCR$LOT/GIPCR$`Patient Days Present`,2)
hist(GIPCR$LOTperPDP,main ="Length of Therapy Per Patient Days Present",xlab="Length of therapy per patient days present",breaks=30)
hist(GIPCR$DOTperPDP,main ="Days of Therapy Per Patient Days Present",xlab="Days of therapy per patient days present",breaks=30)

```


Data per Study Period 

```{r}

table(GIPCR$`Stool Culture Ordered`,GIPCR$`Study Period`)
table(GIPCR$`Stool Culture Results`,GIPCR$`Study Period`)
table(GIPCR$`GI Panel Ordered`,GIPCR$`Study Period`)
tapply(GIPCR$DOT, GIPCR$`Study Period`, mean, na.rm=T)
wilcox.test(GIPCR$DOT~GIPCR$`Study Period`)

```

No difference in median DOT between the two groups 


```{r}

tapply(GIPCR$LOT, GIPCR$`Study Period`, mean, na.rm=T)
wilcox.test(GIPCR$LOT~GIPCR$`Study Period`)

```
No difference in median LOT between the two groups 

```{r}

library(incidence)

```

Now compare the rate of DOT and LOT per PDP 

```{r}
tapply(GIPCR$DOTperPDP, GIPCR$`Study Period`, mean, na.rm=T)


 library(incidence)
library(epiR)
events <- tapply(GIPCR$DOT, GIPCR$`Study Period`, sum,na.rm=T)
events
persontime <- tapply(GIPCR$`Patient Days Present`, GIPCR$`Study Period`, sum,na.rm=T)
persontime
tab_studyperiod <- cbind(events, persontime) 
tab_studyperiod <- tab_studyperiod[c(2,1),]
tab_studyperiod 
epi.2by2(tab_studyperiod, method = "cohort.time")

```
Increase in DOT incidence rate after intrevention (adjusted per patient days)




```{r}
tapply(GIPCR$LOTperPDP, GIPCR$`Study Period`, mean, na.rm=T)
events2 <- tapply(GIPCR$LOT, GIPCR$`Study Period`, sum,na.rm=T)
events2
tab_studyperiod2 <- cbind(events2, persontime) 
tab_studyperiod2 <- tab_studyperiod2[c(2,1),]
tab_studyperiod2
epi.2by2(tab_studyperiod2, method = "cohort.time")

```

Increase in LOT incidence rate after intrevention (adjusted per patient days)

```{r}
library(ggplot2)
p1 <- ggplot(GIPCR,aes(DOT)) + geom_histogram() +facet_wrap(~`Study Period`)
p1
 p2 <- ggplot(GIPCR,aes(LOT)) + geom_histogram() +facet_wrap(~`Study Period`)
p2
p3 <- ggplot(GIPCR,aes(DOTperPDP)) + geom_histogram() +facet_wrap(~`Study Period`)
p3
p4 <- ggplot(GIPCR,aes(LOTperPDP)) + geom_histogram() +facet_wrap(~`Study Period`)
p4

```


 
 
 

